\Title

### 2023-02-20 cover_letter/2023-02-20_coverletter.tex
cover_letter

\begin{quote}
 {\it Key results: Please summarize what you consider to be the outstanding features of the work.}
 Using a single layer of spiking neurons with heterogeneous delays to learn spatio-temporal  spiking motifs
\end{quote} 
\noteRev{We thank Reviewer 2 for its comments. We have thoroughly reworked the manuscript to take them into account.}

@@

\noteRev{Indeed this previous work was not mentioned in the original manuscript as this 4-pages paper was not yet published in the proceedings of the conference in which it was presented. As mentioned in this cover letter and in the previous responses to reviewer \#1, we now added this citation~\cite{grimaldi_2022} and describe the main differences with the submitted study: the use of a more ecological task (section 2.1), a complete formulation of the model (section 2.2) and the ameliroations provided in this particular model (P8, L269). We also cite studies that use similar methods (P7, L243). We also cover more extensive results, notably by testing the learned model with parameterized textures. }

>>>>

\begin{quote}
 {\it Key results: Please summarize what you consider to be the outstanding features of the work.}
 Using a single layer of spiking neurons with heterogeneous delays to learn spatio-temporal  spiking motifs
\end{quote} 
\noteRev{We would like to thank reviewer \#2 for his comments. We have thoroughly revised the manuscript to take them into account.}

@@

\noteRev{In fact, there was no mention of this previous work in the original manuscript, as this 4-page paper had not yet been published in the proceedings of the conference at which it had been presented. As mentioned in the responses to reviewer \#1 in this cover letter, we have now added this citation~\cite{grimaldi_learning_2022}. In addition, in this submitted manuscript we describe the main differences from that previous study: the use of a more ecological task (Section 2.1), a complete formulation of the model (Section 2.2), and the improvements made in this particular model (P8, L269). We also provide citations to studies using similar methods (P7, L243). Further results are presented, especially the testing of the learned model with parametric textures.}
